### 2020-10-20 input/background.tex
a bit of time complexity
meow

\begin{definition}[Dynamic optimal partitioning]
  A dynamic optimal partitioning is an optimal partitioning where the
  set of sources $S$ does not monotonically increase. Process $i$
  joins the set of sources by adding its partition $\alpha_i^{0}$ and
  leaves the set of sources by removing its partition $\delta_i$.
\end{definition}

@@

\begin{problem}[Consistent partitioning]
  \TODO{How to enable \emph{consistent} dynamic optimal partitioning
    with contained broadcast?}
\end{problem}

>>>>

\begin{definition}[Dynamic optimal partitioning]
  A dynamic optimal partitioning is an optimal partitioning where the
  set of sources $S$ does not monotonically increase. We suffix this
  set with \underline{t}ime $t$ : $S(t)$.  Process $i$ joins the set
  of sources by \underline{a}dding its partition with messages
  $\alpha_i^{0}$: $Add(i \not\in S(t)) \implies i \in S(t+1)$; and
  leaves the set of sources by \underline{d}eleting its partition with
  messages $\delta_i$: $Del(i \in S(t)) \implies i \not\in S(t+1)$.
\end{definition}

@@

\begin{problem}[Consistent partitioning]
  \TODO{How to enable \emph{consistent} dynamic optimal partitioning
    in dynamic network with contained broadcast?}
\end{problem}

\TODO{Dynamic Multiple-sources All-destinations shortest path on
  dynamic graphs?}

### 2020-10-20 input/proposal.tex
meow

@@

\textbf{The communication complexity} concerns the size and number of
messages required to reach optimal partitioning. In the average-case,
a process $i$ chosen uniformly at random among all processes creates
a logical partition. Its messages $\alpha_i$ propagate through the
network until reaching processes that belong to another partition
closer to them. This splits partitions in half in average. Overall,
the $a^{th}$ new partition comprises
\smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 a \rfloor}})$}
processes. This decreases every new partition until reaching $0$
processes per new partition: even the chosen process already belongs
to its optimal partition. The average number of messages per process
is \smash{$\mathcal{O}(\frac{\overline{|O|}}{|2^{\lfloor \log_2 a
      \rfloor}})$}.  Deleting the $a^{th}$ partition generates the
exact same number of messages than the $a^{th}$ partition
creation. \TODO{But what about echos?} In the worst-case, every new
partition includes all but one process belonging to the previous
partition. The total number of messages after the $a^{th}$ new
partition is $O(\overline{|O|}\cdot a^2)$. As for the average-case,
the number of messages for the partition deletion is identical to the
number of messages of the corresponding partition creation.

>>>>

A reactive logical partitioning the cost of which actually depends on
its usage.

@@

\textbf{The communication complexity} concerns the size and number of
messages required to reach optimal partitioning. In the average-case,
a process $i$ chosen uniformly at random among all processes creates a
logical partition. Its messages $\alpha_i$ propagate through the
network until reaching processes that belong to another partition
closer to them. This splits partitions in half in average. Overall,
the $a^{th}$ new partition comprises
\smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor \log_2 a \rfloor}})$}
processes. This decreases every new partition until reaching $0$
processes per new partition: even the chosen process already belongs
to its optimal partition. The average number of messages per process
is \smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
      \rfloor}})$}. \TODO{Multiple receipt and multiple delivery imply
  more messages (receipt bounded by $|O|$ as well).} Deleting the
$a^{th}$ partition generates the exact same number of messages than
the $a^{th}$ partition creation. \TODO{But what about echos?} In the
worst-case, every new partition includes all but one process belonging
to the previous partition. The total number of messages after the
$a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot a^2)$. As
for the average-case, the number of messages for the partition
deletion is identical to the number of messages of the corresponding
partition creation.
